---
title: '6051'
author: "Sizheng Zhu"
date: "3/23/2021"
output: html_document
---

Booklet 5

Number of students: 501

The TIMSS Advanced 2015 Mathematics Framework consists of three content domains: (1)algebra, (2)calculus, and (3)geometry. A matrix-sampling approach was used to assemble the pool of advanced mathematics achievement items into a set of 6 assessment booklets, with each student completing one booklet only. 
Data from booklet 5 were utilized in this study. Booklet 5 consisted of 3 blocks(M5, M8 and M9). It contained responses from 501 students to 40 items with 12 items on algebra, 18 items on calculus and 10 items on geometry. Omitted responses and partially correct responses were treated as incorrect in this study.


#Data cleaning

```{r}
#install.packages("haven")
library(haven)

data = read_sav("MSAUSAM3.sav")
#####
str(data)

book5<-data[data$IDBOOK==5,]

book5_1<-book5[,c(55:65,91:119)]

book5_2<-book5_1

book5_2[is.na(book5_2)] <- 0

###
###M5

book5_2$MA23144<-ifelse(book5_2$MA23144==3,"1","0")
book5_2$MA23185<-ifelse(book5_2$MA23185==1,"1","0")
book5_2$MA23054<-ifelse(book5_2$MA23054%in%c(20,21),"1","0")
book5_2$MA23064<-ifelse(book5_2$MA23064==1,"1","0")
book5_2$MA23131A<-ifelse(book5_2$MA23131A==10,"1","0")
book5_2$MA23131B<-ifelse(book5_2$MA23131B%in%c(10,11),"1","0")
book5_2$MA23157<-ifelse(book5_2$MA23157==20,"1","0")
book5_2$MA23045<-ifelse(book5_2$MA23045==3,"1","0")
book5_2$MA23082<-ifelse(book5_2$MA23082==1,"1","0")
book5_2$MA23020<-ifelse(book5_2$MA23020==4,"1","0")
book5_2$MA23094<-ifelse(book5_2$MA23094%in%c(20,21,22),"1","0")


###M8
book5_2$MA33091<-ifelse(book5_2$MA33091==10,"1","0")
book5_2$MA33106<-ifelse(book5_2$MA33106==2,"1","0")
book5_2$MA33090<-ifelse(book5_2$MA33090==20,"1","0")
book5_2$MA33126<-ifelse(book5_2$MA33126==2,"1","0")
book5_2$MA33118A<-ifelse(book5_2$MA33118A==1,"1","0")
book5_2$MA33118B<-ifelse(book5_2$MA33118B==3,"1","0")
book5_2$MA33118C<-ifelse(book5_2$MA33118C==2,"1","0")
book5_2$MA33118<-ifelse(book5_2$MA33118==20,"1","0")
book5_2$MA33243<-ifelse(book5_2$MA33243%in%c(20,21),"1","0")
book5_2$MA33229<-ifelse(book5_2$MA33229==10,"1","0")
book5_2$MA33011<-ifelse(book5_2$MA33011==1,"1","0")
book5_2$MA33159<-ifelse(book5_2$MA33159==10,"1","0")
book5_2$MA33054<-ifelse(book5_2$MA33054==4,"1","0")


####M9
book5_2$MA33085<-ifelse(book5_2$MA33085==4,"1","0")
book5_2$MA33190<-ifelse(book5_2$MA33190==10,"1","0")
book5_2$MA33115<-ifelse(book5_2$MA33115==3,"1","0")
book5_2$MA33237<-ifelse(book5_2$MA33237==10,"1","0")
book5_2$MA33077<-ifelse(book5_2$MA33077==1,"1","0")
book5_2$MA33132<-ifelse(book5_2$MA33132==1,"1","0")
book5_2$MA33218<-ifelse(book5_2$MA33218==20,"1","0")
book5_2$MA33236A<-ifelse(book5_2$MA33236A==3,"1","0")
book5_2$MA33236B<-ifelse(book5_2$MA33236B==2,"1","0")
book5_2$MA33236C<-ifelse(book5_2$MA33236C==1,"1","0")
book5_2$MA33236D<-ifelse(book5_2$MA33236D==2,"1","0")
book5_2$MA33236<-ifelse(book5_2$MA33236==20,"1","0")
book5_2$MA33181<-ifelse(book5_2$MA33181==3,"1","0")
book5_2$MA33002<-ifelse(book5_2$MA33002==10,"1","0")
book5_2$MA33169<-ifelse(book5_2$MA33169==2,"1","0")
book5_2$MA33235<-ifelse(book5_2$MA33235==10,"1","0")


cols.num <- c(colnames(book5_2))

book5_2[cols.num] <- sapply(book5_2[cols.num],as.numeric)

Alg<-book5_2[,c(1:5,12:14,25:28)]
Cal<-book5_2[,c(6:8,15:21,29:36)]
Geo<-book5_2[,c(9:11,22:24,37:40)]

data_scored<-cbind(Alg,Cal,Geo)
cbind(Alg,Cal,Geo)

###subscore pacakge
library(subscore)

#generate the data list for the main function
prep1<-data.prep(data_scored,c(3,12,18,10),
                         c("Algebra","Calculus","Geometry", "Math"))

```


###Haberman's methods 
```{r}

# Estimating subscores using Haberman's methods       
CTTsub(prep1,method="Haberman")

# Obtaining raw subscores  
CTTsub(prep1,method="Haberman")$subscore.original  

# Obtaining descriptive statistics summary for estimated subscores  
CTTsub(prep1,method="Haberman")$summary 

# Obtaining original correlation for the three methods
CTTsub(prep1,method="Haberman")$Correlation  

# Obtaining disattenuated correlation for the three methods
CTTsub(prep1,method="Haberman")$Disattenuated.correlation  

# Obtaining PRMSEs for the three methods
CTTsub(prep1,method="Haberman")$PRMSE  

# Obtaining subscores that are estimated as a function of the observed subscores 
CTTsub(prep1,method="Haberman")$subscore.s 

# Obtaining subscores that are estimated as a function of the observed total score 
CTTsub(prep1,method="Haberman")$subscore.x  

# Obtaining subscores that are estimated as a function of both the observed subscores and the observed total score.
CTTsub(prep1,method="Haberman")$subscore.sx  

# Hypothesis test
CTTsub(prep1,method="Haberman")$PRMSE.test

```

#Wainer's method

```{r}
# Estimating subscores using Wainer's method
CTTsub(prep1,method="Wainer") 
       
# Obtaining descriptive statistics summary for subscores
CTTsub(prep1,method="Wainer")$summary   

# Obtaining original subscores
CTTsub(prep1,method="Wainer")$subscore.original 

# Obtaining subscores that are estimated using Wainer's augmentation method  
CTTsub(prep1,method="Wainer")$subscore.augmented  

```

